Supplementary Materials to ``Recurrent event analysis in the presence of real-time high frequency data via random subsampling''

### 2023-05-22 letters/response-ref-1-v1.tex

{\bf Response to Referees}

We appreciate all of the very helpful comments from the editor, associate editor, and the two referees which has helped improve the paper substantially. We have addressed the concerns as best as possible in this revision. We provide a further point-by-point explanation below. Any comments in {\it italics} indicate a statement from the referee report.

{\bf Response to Associate Editor}
\begin{enumerate}
\item {\it This paper was reviewed by two referees, who tend to agree in their positive assessments of the value and novelty of your work, and provide some very specific comments for further improvements.}

\vspace{5mm}
We thank the associate editor.  We have addressed the two reviewers' specific comments.  Responses to their concerns are detailed below and have significantly improved the clarity of this manuscript.   All major edits are highlighted in blue in order to help the referees know what has changed as part of the major revision.
% CHECK
\vspace{5mm}

@@

\item {\it Expanded literature review on existing modeling approaches. Both referees raise this point, and I agree that the contrast with existing works could be more explicit. The second referee provides some specific suggestions on relevant works.}

\vspace{5mm}
We have added a detailed discussion of related work in Section 1.1, which includes the specific suggestions on relevant works provided by the second referee; specifically, we discuss recent modeling of time-to-event data with functional covariates as well as joint modelling from a functional regression perspective.  We contrast these approaches with our design-based approach which becomes necessary when considering high-frequency sensor processes rather than traditional longitudinal studies as the number of measurement occasions increase from tens to thousands/millions of times per individual.  We connect and contrast our use of subsampling with the general use of subsampling in handling massive data and its recent use in massive data with functional predictors.  As stated by the second referee, our proposed joint model uses a recent history functional linear model which we now link with the previous work by Damla Senturk and others.  This motivates Section 5.2 which provides an additional empirical study and discussion of the tuning parameter~$\Delta$.
% CHECK
\vspace{5mm}

@@

\item {\it There appear to be some missing definitions of notation, and some transitions/equations need more details to justify them. The latter could potentially be put in the supplement to save space. The former should be added to the main manuscript to improve clarity.}

\vspace{5mm}
We have addressed the missing notation and helped to justify the transitions/equations.  These additions are highlighted in blue.
\vspace{5mm}

\item {\it As the first reviewer, I am confused by $\varepsilon(t) = 0$ on page 4, line 39, in line with equation (3) and measurement error methodology. I suspect comment 7 from the 2nd reviewer alludes to the same thing. I suspect this may be a notation issue rather than the modeling issue, but either way, it needs to be clarified.}

\vspace{5mm}
We have decided that the point we were trying to raise is not essential to the main manuscript, so we have moved the discussion of \emph{independent evolution} and its implication that $\varepsilon (t) = 0$ for all $t >0$ to Appendix B.  The key issue we were trying to clarify is that the traditional joint model formulation in which the observed health process and time-to-event are conditionally independent given the latent process implies that the hazard function conditional on the entire observed health process depends on values after the current time.  In the case study, for example, this implies that the expected risk of a button press given the entire sensor process will depend on future activity index and electrodermal activity.  This holds unless we assume the measurement error is set to zero.  While we still think it is an important point that should be more well appreciated in the joint modeling literature, the current paper has enough content for this discussion to be left to the appendix.  Moreover, the empirical impact seems to be limited and therefore it is better to make this point in less central to the current manuscript.
\vspace{5mm}

@@

\item {\it Practical considerations, such as window size and smoothing parameter selection, need clarification.}

\vspace{5mm}
We added Section 5.2 to discuss choice of window size; specifically, we consider selection based on Akaike information criteria as part of the simulation study rather than simply the impact of incorrect choice of $\Delta$. Table 4 shows that when inference is sensitive to bandwidth selection, the adaptive tuning of $\Delta$ based on AIC does perform well empirically.  We now use this approach in selecting~$\Delta$ in the case study, and provide AIC and BIC across several choices of $\Delta$ in Table 6.
\vspace{5mm}

@@

The smoothing parameter selection is also discussed in Section 4.6; given our connection to off-the-shelf penalized logistic regression, the smoothing parameter selection occurs as part of this implementation.  In the R package we are using, `glmnet', the smoothness parameter is chosen via cross-validation.
\vspace{5mm}

\item {\it Reviewer 2 suggests adding additional details on proof steps and lemma clarifications. I can't entirely agree that the proofs should go in the main manuscript as the paper is already on the longer side. When making adjustments to this section (theoretical analysis), please keep at most its current length, and move things to supplement as needed.}

\vspace{5mm}
To accommodate the second referee's request without making the discussion too long, we have re-written the technical proofs to include the intuition and integrated this with our detailed proof. We point the interested reader to these details in the main paper.  We hope this helps the reader develop intuition on the first read while giving them some helpful guidance in order to facilitate understanding of the detailed theoretical analysis.
\vspace{5mm}

@@

\item {\it Both reviewers suggest additional simulation studies. I agree that it would be good to have a numerical benchmark of the magnitude of the computational issue that you allude to in lines 16-28 on page 5, especially for JCGS readership. I don’t think you need references for this, as the reviewer asks, as a numerical example would be more helpful and convincing in this case. However, I think you need another method for comparison, as the simulations are only done for your approach with different sampling rates. Perhaps some suggestions from the first referee could be useful. If some of these alternatives are computationally prohibitive, then doing a computational numerical comparison on even 1 rep will provide a convincing argument for why those methods are not tried.}

\vspace{5mm}
As far as the author is aware, there does not exist a joint modeling package that can estimate the proposed model directly; one way would be to assume you know the functional form of the parameter but not the scale.  Comparison of measures of bias, estimation accuracy, and numerical speed under this approach to our methodology which learns the functional form are likely inappropriate. To address the reviewers concern, we now highlight the extent of the numerical issues in Remark 5.1.  Specifically, running a traditional joint model will take a similar time to running our approach under very high subsampling frequencies, i.e., at the sensor measurement rate.  We now subsample at a rate of every five minutes, fifteen minutes, thirty minutes, one hour, and two hours in our simulation section.  Using a time-complexity analysis (supported by the simulations), we can extrapolate run times when sampling at 4Hz to a standard joint model needing approximately 2 and 6.2 hours to run in our two settings respectively; at 32Hz this would be 16 and 50.1 hours respectively. These are extremely high run times when we compare to a run-time of 1.8 and 3.5 minutes when subsampling at rate of every fifteen minutes.  Moreover, the benefits in terms of variance, squared bias, and MISE appear almost negligible.
\vspace{5mm}

@@

\item {\it I also have additional comments that were not raised. A major one is the absence of code. A user-friendly software with the method’s implementation and documentation is a must for accepted JCGS papers. Please provide the code so that the results are reproducible.}

\vspace{5mm}
We apologize for this omission.  Upon original submission, we had a GitHub repository that included both our code and documentation.  We did not cite the repository simply because other journals ask for anonymous submissions which means the GitHub link needs to be removed.  Given JCGS does not require this, we have now cited the repository in the Appendix.  The GitHub repository has been improved to include better documentation to ensure users of our proposed method can properly implement our solution on their own problems. Again we apologize for not correcting this before originally submitting the article. We think the revision now meets the standards of JCGS papers in terms of user-friendly software.
\vspace{5mm}

\item {\it
A minor one is the absence of truncation $K_x$ in the equation on line 37, page 8. Please reread everything carefully to ensure all notations are defined and the equations are consistent with the text.}

\vspace{5mm}
We apologize for this omission. We have reread everything and addressed any missing notation and equation consistency.  Moreover, we have added a notation glossary in the Appendix.
\vspace{5mm}

@@

\item {\it Another minor one is your choice of smoothing the entire covariance, including the diagonals (page 8, lines 13-18). It’s unclear to me what the rationale is for changing this step compared to Park and Staicu, 2015, and how much it matters for the final performance.}

\vspace{5mm}
We have moved the discussion of \emph{independent evolution} to the Appendix.  While the author still thinks it an important point that he wishes was more well appreciated in the joint modeling literature, the current paper has enough content for this discussion to be omitted from the main paper.
\vspace{5mm}

@@

I am very grateful to the referee for the incredibly detailed review.  The detailed suggestions and comments helped improve the paper in numerous ways.  See below for our responses to each particular reviewer comment.

\begin{enumerate}
\item {\it The introduction it quite lacking. Please add more background literature review of prevailing/latest approaches (particularly in the area of joint modeling of longitudinal and time to event data) to the introduction.}

\vspace{5mm}
We have added a detailed discussion of related work in Section 1.1, which includes the specific suggestions on relevant works provided by the second referee; specifically, we discuss recent modeling of time-to-event data with functional covariates as well as joint modelling from a functional regression perspective.  We contrast these approaches with our design-based approach which becomes necessary when considering high-frequency sensor processes rather than traditional longitudinal studies as the number of measurement occasions increase from tens to thousands/millions of times per individual.  We connect and contrast our use of subsampling with the general use of subsampling in handling massive data and its recent use in massive data with functional predictors.  As stated by the second referee, our proposed joint model includes a recent history functional linear model which we now link with the previous work by Damla Senturk and others.  This motivates Section 5.2 which provides an empirical study of choosing the tuning parameter~$\Delta$ using an AIC-based selection criteria.
\vspace{5mm}

\item {\it The measurement error part can be added to the end with other extensions. It does not seem to play a major role in developing the algorithm.}

@@

\vspace{5mm}
We agree.  This point was over-emphasized in the original manuscript. We have decided that the point we were trying to raise is non-essential to the current manuscript, so we have removed the discussion of \emph{independent evolution} and its implications.
\vspace{5mm}

\item {\it In equation (4), page 4, do you mean that equation (2) and the mesurement error part $x_i (t) = \eta_i (t) + \epsilon_i (t)$ imply conditional hazard equation in (3)?  If yes, then why is $\int_{t-\Delta}^t \epsilon_i (s) \beta(s) ds = 0$?  Or are you assuming a model?  Please add more clarity.}

\vspace{5mm}
We have now moved this part from the current manuscript to the Appendix. The key issue we were trying to clarify is that the traditional joint model formulation in which the observed health process and time-to-event are conditionally independent given the latent process implies that the hazard function conditional on the entire observed health process depends on values after the current time.  In the case study, for example, this implies that the expected risk of a button press given the entire sensor process will depend on future activity index and electrodermal activity.  This holds unless we assume the measurement error is set to zero.  In this setting,~$\epsilon_i (t) = 0$ and so $\int_{t-\Delta}^t \epsilon_i (s) \beta(s)ds = 0$ by definition. While the author still thinks it an important point that he wishes was more well appreciated in the joint modeling literature, the current paper has enough content for this discussion to be moved from the main paper to the Appendix.  Moreover, the empirical impact seems to be limited and therefore it is better to make this point less central to the main manuscript.
\vspace{5mm}

@@

\item {\it Several notations in section 2.1 such as ${\bf x}_i, {\bf H}_{i,\tau_i}^X$ are not defined.}

\vspace{5mm}
Both of these were defined in Section 3 but we agree that the definitions were obscured in the writing, which led to confusion.  To address this, we have added a notation glossary as Appendix A.
\vspace{5mm}

@@

\item {\it In line 39, page 4, by assuming $\epsilon(t) = 0$, you assume there is no measurement error? Why is section 2.1 called measurement error if the error is 0? Should this be named missing data section instead?}

\vspace{5mm}
The key point raised on page 4 of the original submission is that if $\epsilon(t)$ is not equivalently zero, your model assumes risk of an event at time $t$ depends on both the current and future measurements of the process ${\bf x}_i$. We argue this is not sensible since current risk should not depend on future risk and thus set $\epsilon(t) = 0$.  This discussion is now in Appendix B.
\vspace{5mm}

\item  {\it Is $\theta$ defined anywhere prior to section 2.2?}

\vspace{5mm}
It was used in equation (1) to refer to all the parameters underlying the model to distinguish it from the functional parameter~$\beta (s)$. We have added a notation glossary in Appendix A, and re-iterate its definition in Section 3 to make this clearer.
\vspace{5mm}

@@

\item {\it Check the notation in equation (6) page 6. Some subscripts seem to be missing. Add some details on how to obtain this from the original score
equation. What is the approximation here?}

\vspace{5mm}
We have included correct subscripts in the revision.  Derivation of (6) follows from plugging in (4) into equation the score equations.  We now make this clear and provide a derivation in the supplementary materials for completeness.
\vspace{5mm}

\item{\it The remark 2.1 can be added the end of section 2.2. This along with
comment 8 will naturally lead the way your proposed method.}

\vspace{5mm}
We thank the referee for this suggestion.  We have now used Remark 2.1 and comment 8 on the computational costs to improve the end of section 2.2 and motivate our proposed method.
\vspace{5mm}

@@

\item {\it Page 7, line 48, in the definition of the marginal covariance, what is $\tau$?}

\vspace{5mm}
The term $\tau$ refers to the censoring time of the observation process. We make this clear in page 4 in Section 3 and pages 8--9 in Section 4.1 of the revision.
\vspace{5mm}

\item {\it Is there a difference between the mean and covariance functions for $y = 0$ and $y = 1$ especially if points in $D_i$ and $T_i$ are spread roughly evenly on a grid even if the sets are disjoint? For example, pick a grid of equidistant points and number them from $1-10$. If all odd points are events in $T_i$ and even ones are sampled in $D_i$, won't the pooled sample covariance for both be the same}

\vspace{5mm}
The event times~$T_i$ depend heavily on the event intensity function~$h_i (t;\theta)$ and will not be guaranteed to be uniformly spread across points in $[0,\tau]$.  The subsampling times~$D_i$ depend on the subsampling intensity function~$\pi_i(t)$; under the assumption that $\pi_i (t) = \lambda$, we can view this as first drawing the number of non-event times from a Poisson distribution, i.e., $| D_i | \sim Poisson(\lambda)$, and then independently selecting $|D_i|$ non-event times uniformly at random over the observation window~$[0, \tau_i]$.  Given the potential difference between the distributions, we choose to model the mean and covariance functions separately to ensure good approximation when applying the spectral decomposition of the estimated covariance function.  To illustrate this, Figure 2 in Appendix D.3 presents mean curves for EDA and AI over the same 30 minute window.  These figures demonstrate quite distinct behavior. Another reason for treating these two distinctly is that the missing data imputation from Petrovich et al. (2018) requires distinct covariance functions.  given the potential difference between the distributions, we choose to model the mean and covariance functions separately to ensure good approximation when applying the spectral decomposition of the estimated covariance function.  To illustrate this, Figure 2 in Appendix D.3 presents mean curves for EDA and AI over the same 30 minute window.
\vspace{5mm}

@@

\item {\it Add a plot of the mean, covariance functions for $y=0$ and $y=1$.}

\vspace{5mm}
Figure 2 in Appendix D.3 presents mean curves for EDA and AI over the same 30 minute window.  The covariance functions did not plot well and given the point regarding need of modeling $y=0$ and $y=1$ separately is answered by the simpelr mean plot, we omitted the covariance function plots.
\vspace{5mm}

@@

\vspace{5mm}
We have added Remark 4.5 to provide a simple example where these assumptions are satisfied.  Specifically, if individuals are assumed independent and identically distributed, the functional process is bounded (i.e., $|X(t,s)| < M$), and the subsampling rate is both lower and upper bounded at all risk times then we are guaranteed to have Assumptions 4.3 and 4.4. Boundedness is likely to be true in most practical settings and thus demonstrates the reasonableness of our assumptions for applied settings.
\vspace{5mm}

\item {\it All the modes of convergences in Lemma 3.5 and its proofs should be made clear.}

\vspace{5mm}
We have now clarified that the convergence is in law as the number of individuals goes to infinity.  Proofs are also clarified accordingly.
\vspace{5mm}

\item {\it Outline the proof of Lemma 3.5 first and then prove the details.  It will be easier to follow.}

\vspace{5mm}
We have added intuition to the detailed proofs where necessary and highlighted these edits in blue.  We think this will help the reader understand the proof at a high-level and then the interested reader can delve into the technical details.
\vspace{5mm}

@@

\item {\it In Lemma 3.6 state the theorem clearly.  What condition do yu show in the proof that establishes optimality}

\vspace{5mm}
We have now included the statement of how we define optimality in the main paper to make the theorem statement clear.  Specifically, we view weights $w^\star$ as optimal if the difference between the asymptotic variance~$V (\theta_0; w^\star)$ and the asymptotic variance under any other choice of weights~$w$, $V(\theta_0; w)$ is positive semi-definite. The proof is kept in the supplementary materials for conciseness.
\vspace{5mm}

\item {\it Combine section 3.6 and 3.7 into a single result that establishes a confidence band for $\beta (t)$. Also, wont Lemma 3.5 lead to a confidence band for $\hat \beta (t)$? Are the two bands same?}

@@

\vspace{5mm}
We have moved the discussion of confidence bands to follow Lemma 3.5 (now 4.5) given that it is directly a consequence of the asymptotic result.  We then  discuss penalization in a subsequent section which is employed due to the potential complexity induced by choosing $K_b$ large enough for the assumption $\beta (t) =\phi (t) b^\star$ to hold.
\vspace{5mm}

\item {\it The ``original'' score equation Page 5, line 9 involves
$$
H_i (\tau_i ;\theta) = \int_{t=0}^{\tau_i} h_i (t; \theta)dt = \int_0^{\tau_i} \left[ h_0 (t;\gamma) \exp \left( g_t (H_{i,t}^N)^\top \alpha + \int_{s=t-\Delta}^t x_i (s) \beta(t) ds \right) \right] dt
$$
In the subsampled version you suggest in equation 6, page 6, you essentially replace $H_i (\tau_i; \theta)$ computation with $h_i (u; \theta)$, $u \in D_i$. How much time would it take to solve the full likelihood equation that will involve the above equation (1) directly? With the basis expansion strategy, you
would will be estimating the same number of parameters. This type of approach should be added to simulations and evaluated for accuracy and time complexity.}

\vspace{5mm}
We really appreciate this question which has helped clarify an important element of the paper.  To address this question, we have added Remark 5.1 to evaluate the accuracy and time complexity.  We recap some of our discussion here for convenience.
\vspace{5mm}

### 2023-05-22 write-up/fda-recurrent-supplement.tex
updated main and supp papers

\documentclass[12pt]{amsart}
\usepackage{amsmath}
\usepackage{tikz}
\usetikzlibrary{matrix,arrows}
\usepackage{amsfonts,amssymb,amsthm, txfonts, pxfonts,amscd}
\usepackage[stretch=10]{microtype}
%\usepackage{hyperref}
\def\struckint{\mathop{%
\def\mathpalette##1##2{\mathchoice{##1\displaystyle##2}%
 {##1\textstyle##2}{##1\scriptstyle##2}{##1\scriptscriptstyle##2}}%
\mathpalette
{\vbox\bgroup\baselineskip0pt\lineskiplimit-1000pt\lineskip-1000pt
\halign\bgroup\hfill$}
{##$\hfill\cr{\intop}\cr\diagup\cr\egroup\egroup}%
}\limits}
\usepackage{natbib}
\usepackage{color}
\usepackage{booktabs,caption,fixltx2e}
\usepackage[flushleft]{threeparttable}
\usepackage{amsmath}
\usepackage{tikz}
\usetikzlibrary{matrix,arrows}
\usepackage{amsfonts,amssymb,amsthm, txfonts, pxfonts,amscd}
\usepackage{multirow}
\usepackage{floatrow}
\usepackage{subcaption}
% Table float box with bottom caption, box width adjusted to content
\newfloatcommand{capbtabbox}{table}[][\FBwidth]

@@

@@

\section{Derivation of the design-unbiased score equations}
\label{app:prooflemma31}

@@

\begin{proof}[Proof of Lemma~\ref{lemma:simpleasym}]
% Lemma~\ref{lemma:simpleasym} will be proven under regularity conditions A-E in~\cite[pp. 420--421]{Andersen1993} along with the following assumptions related to the subsampling rate~$\pi_i (t)$.
Define the joint counting process
\[
M_i (t) = N_i (t) - \int_0^t (h_i (s; \theta) + \pi_i (s)) R_i (s) ds.
\]
where~$N_i (t)$ is the counting process with jumps at all~$t \in \bfT_i \cup \bfD_i$. Asymptotic consistency is guaranteed~\cite[Theorem VI.1.1]{Andersen1993} if
\begin{equation}
\label{eq:andersen1}
n^{-1} \tilde U_n (\theta_0 ) \overset{P}{\to} 0,
\end{equation}
and
\begin{equation}
\label{eq:andersen2}
n^{-1} \frac{d}{d \theta^{\top}} \tilde U_n (\theta) \big |_{\theta =
  \theta_0} = \Xi (\theta),
\end{equation}
and
\begin{equation}
\label{eq:andersen3}
\lim_{n \to \infty} P \left( \left | n^{-1} \frac{d^2}{d \theta_j d
      \theta_k} \tilde U_n (\theta) \right | < M \text{ for all }
  j,k \text{ and all } \theta \in \Theta_0 \right) = 1
\end{equation}
To prove~\eqref{eq:andersen1}, we decompose~$\tilde U_n (\theta_0)$ into
three terms
\begin{equation}
\label{eq:decomp}
n^{-1} \tilde U_n (\theta_0) = n^{-1} U_n (\theta_0 )  + n^{-1} \left(
  \hat U_n (\theta_0) - U_n (\theta) \right) + n^{-1} \left(\tilde U_n
  (\theta_0) - \hat U_n (\theta_0) \right)
\end{equation}
where, recall,~$\hat U_n (\theta_0)$ are the logistic score equations with $\int_0^\infty X_i(t,s) \beta(s) ds$ and~$\tilde U_n (\theta_0)$ with the approximation~$C_{i,t}^\top J_{\phi, \psi} {\bf b}$. \cite{Andersen1993} (Theorem VI.1.1) show that~$n^{-1} U_n (\theta_0)
\to 0$. The second term
\begin{align*}
n^{-1} \left( \hat U_n (\theta_0) - U_n (\theta_0) \right) =
  \frac{1}{n} \sum_{i=1}^n \int_0^{\tau} \frac{h^{(1)} (s;
  \theta_0)}{\pi_i (s) + h (s;\theta_0)} d M_i (s).
\end{align*}
where~$h(\cdot; \theta_0)$ is given by~\eqref{eq:hazardlinear}. Lenglart's inequality implies the second term converges in probability to zero under Assumptions~\ref{E1} and~\ref{E2}. The third term satisfies
\begin{align*}
  &n^{-1} \left \| \hat U_n (\theta_0) - \tilde U_n (\theta_0) \right \| \\
  \leq & M n^{-1} \sum_{i=1}^n \sum_{t \in \bfT_i \cup \bfD_i} \bigg \| g
         \left( \tilde W_{i,t}^\top \theta  + \sum_{k=K_x+1}^\infty \hat
         c_{i,k} (t) \int_{t-\Delta}^t \hat \psi_k (s) \phi (s)^\top b
         + \log (\pi_i (t) ) \right) - g \left( \tilde W_{i,t}^\top
         \theta + \log (\pi_i (t)) \right) \bigg \| \\
&\leq M n^{-1} \sum_{i=1}^n \sum_{t \in \bfT_i \cup \bfD_i}
    \sup_{x \in \mathbb{R}} \left \| g^\prime \left( x \right)
  \right\| \times \left \| \sum_{k=K_x+1}^\infty \hat c_{i,k} (t)
  \sum_{l=1}^{K_b} \int_{t-\Delta}^t \hat \psi_k (s) \phi_l (s) b_l
  \right \| \\
&= \frac{M}{4} n^{-1} \sum_{i=1}^n \sum_{t \in \bfT_i \cup \bfD_i}
  \sum_{l=1}^{K_b} \left \| \int_{t-\Delta}^t
  \left( X(t,s) - \sum_{k=1}^{K_x} \hat c_{i,k} (t) \psi_k (s) \right)
  \phi_l (s) b_l\right \| \\
&\to \frac{M}{4} \int_0^\tau \sum_{l=1}^{K_b} \left \| \int_{t-\Delta}^t
  \left( X(t,s) - \sum_{k=1}^{K_x} \hat c_{i,k} (t) \psi_k (s) \right)
  \phi_l (s) b_l\right \| (f_0(t) + f_1(t)) dt
\end{align*}
where~$M = \sup \| \tilde W_{i,t} \|$,~$g(x) = 1/(1+\exp(-x))$ is the
expit function.
The second inequality is due to the Taylor remainder theorem. The third is due to~$g^\prime (x) = e^x/(1+e^x)^2 \leq e^0/(1+e^0)^2 = 1/4$, reordering the summation, and rewriting the error term in terms of the difference between~$X(t,s)$ and the approximation with truncation level~$K_x$. Letting~$n \to \infty$ allows us to re-write the outside sums in terms of the integrated difference where the integral is with respect to the joint event and sampling distributions~$(f_0(t) + f_1 (t))$. Finally, under Assumptions~\ref{assumption:truncation}, \cite{Park2018} show
\[
X(t,s) - \sum_{k=1}^{K_x} \hat c_{i,k} (t) \psi_k (s) \overset{P}{\to} 0
\]
as~$K_x \to \infty$, which implies the third term goes to zero as the truncation level goes to infinity. The same argument can be used in conjunction under assumptions~\ref{E1} and~\ref{E4} to prove~\eqref{eq:andersen2}.

@@

>>>>

\documentclass[12pt]{amsart}
\usepackage{amsmath}
\usepackage{tikz}
\usetikzlibrary{matrix,arrows}
\usepackage{amsfonts,amssymb,amsthm, txfonts, pxfonts,amscd}
\usepackage[stretch=10]{microtype}
%\usepackage{hyperref}
\def\struckint{\mathop{%
\def\mathpalette##1##2{\mathchoice{##1\displaystyle##2}%
 {##1\textstyle##2}{##1\scriptstyle##2}{##1\scriptscriptstyle##2}}%
\mathpalette
{\vbox\bgroup\baselineskip0pt\lineskiplimit-1000pt\lineskip-1000pt
\halign\bgroup\hfill$}
{##$\hfill\cr{\intop}\cr\diagup\cr\egroup\egroup}%
}\limits}
\usepackage{natbib}
\usepackage{color}
\usepackage{booktabs,caption,fixltx2e}
\usepackage[flushleft]{threeparttable}
\usepackage{amsmath}
\usepackage{tikz}
\usetikzlibrary{matrix,arrows}
\usepackage{amsfonts,amssymb,amsthm, txfonts, pxfonts,amscd}
\usepackage{multirow}
\usepackage{floatrow}
\usepackage{subcaption}
% Table float box with bottom caption, box width adjusted to content
\newfloatcommand{capbtabbox}{table}[][\FBwidth]
\newenvironment{newmaterial}{\color{blue}}{\par}

@@

\section{Notation Glossary}
\label{app:notation}

\begin{newmaterial}

\begin{itemize}
\item[${\bf T}_i$] \quad Observed event times on individual $i$.
\item[$\tau_i$] \quad Observation window-length for individual $i$
\item[$N_i(t)$] \quad Counting process associated with ${\bf T}_i$
\item[${\bf x}_i$] \quad Health process for individual $i$, i.e., $\{ x_i (s) \}_{0 < s <\tau_i} \}$
\item[$H_{i,t}^{NX}$] \quad The $\sigma$-field generated by all past values $(N_i(s), x_i(s))_{0 \leq s \leq t}$
\item[$h_i (t| H_{i,t}^{NX}; \theta)$] \quad Fully parametric conditional hazard function
\item[$h_0 (t; \gamma)$] \quad Parametrized baseline hazard function
\item[$\Delta$] \quad An unknown, window-length
\item[$\theta$] \quad All parameters underlying this hazard function including baseline parameters~$\gamma$, event-history and time-in-study parameters~$\alpha$, and the functional parameter $\{ \beta(s) \}_{0 \leq s \leq \Delta}$.
\item[$H_i (t; \theta)$] \quad Cumulative hazard function
\item[$U_n (\theta)$] \quad True score equations for log-likelihood of the event process
\item[${\bf D}_i$] \quad Sampled non-event times on individual $i$.
\item[$\hat H_i^{(1)} (t; \theta)$] \quad Waagepetersen estimator of the cumulative hazards using all $u \in {\bf T}_i \cup {\bf D}_{i}$
\item[$\hat U_n (\theta)$] \quad Approximate estimating equations leveraging the Waagepetersen estimator
\item[$\Sigma_y (s,s')$] \quad Marginal covariance over event or subsampling intensity $f_y (T)$
\item[$\mu_y (t,s)$] \quad Mean function $s$ time units before time $t$
\item[$\tilde U_n (\theta)$] \quad Approximate estimating equations leveraging both subsampling and functional data approximations
\end{itemize}

\end{newmaterial}

@@

\section{Technical Arguments}

\subsection{Derivation of the design-unbiased score equations}
\label{app:prooflemma31}

@@

\subsection{Proof of Lemma~\ref{lemma:simpleasym}}
\label{proof:asymp}

\begin{newmaterial}
We break the proof of Lemma~\ref{lemma:simpleasym} into two sections.  First, we prove asymptotic consistency, i.e.,~$\hat \theta_n \to \theta_0$ in probability as $n \to \infty$ and $K_x \to \infty$.  Then, we prove asymptotic normality via Rebolledo's martingale central limit theorem.
\end{newmaterial}
\begin{proof}[Proof of asymptotic consistency]
% Lemma~\ref{lemma:simpleasym} will be proven under regularity conditions A-E in~\cite[pp. 420--421]{Andersen1993} along with the following assumptions related to the subsampling rate~$\pi_i (t)$.
Define the joint counting process
\[
M_i (t) = N_i (t) - \int_0^t (h_i (s; \theta) + \pi_i (s)) R_i (s) ds.
\]
where~$N_i (t)$ is the counting process with jumps at all~$t \in \bfT_i \cup \bfD_i$. Asymptotic consistency is guaranteed~\cite[Theorem VI.1.1]{Andersen1993} if
\begin{equation}
\label{eq:andersen1}
n^{-1} \tilde U_n (\theta_0 ) \overset{P}{\to} 0,
\end{equation}
and
\begin{equation}
\label{eq:andersen2}
n^{-1} \frac{d}{d \theta^{\top}} \tilde U_n (\theta) \big |_{\theta =
  \theta_0} = \Xi (\theta),
\end{equation}
and
\begin{equation}
\label{eq:andersen3}
\lim_{n \to \infty} P \left( \left | n^{-1} \frac{d^2}{d \theta_j d
      \theta_k} \tilde U_n (\theta) \right | < M \text{ for all }
  j,k \text{ and all } \theta \in \Theta_0 \right) = 1
\end{equation}
To prove~\eqref{eq:andersen1}, we decompose~$\tilde U_n (\theta_0)$ into
three terms
\begin{equation}
\label{eq:decomp}
n^{-1} \tilde U_n (\theta_0) = \underbrace{n^{-1} U_n (\theta_0 )}_{(I)}  + \underbrace{n^{-1} \left(
  \hat U_n (\theta_0) - U_n (\theta) \right)}_{(II)} + \underbrace{n^{-1} \left(\tilde U_n
  (\theta_0) - \hat U_n (\theta_0) \right)}_{(III)}
\end{equation}
where, recall,~$\hat U_n (\theta_0)$ are the logistic score equations with $\int_0^\infty X_i(t,s) \beta(s) ds$ and~$\tilde U_n (\theta_0)$ with the approximation~$C_{i,t}^\top J_{\phi, \psi} {\bf b}$.
\textcolor{blue}{This decomposes the term into (I) the original score equations which we are known to yield asymptotically consistent estimates, (II) the difference between the original score equations and the design-unbiased score equations, and (III) the design-unbiased score equations with and without the approximation using the Karhunen-Loeve decomposition and~$K_x < \infty$.}

\cite{Andersen1993} (Theorem VI.1.1) show that~$n^{-1} U_n (\theta_0)
\to 0$. The second term
\begin{align*}
n^{-1} \left( \hat U_n (\theta_0) - U_n (\theta_0) \right) =
  \frac{1}{n} \sum_{i=1}^n \int_0^{\tau} \frac{h^{(1)} (s;
  \theta_0)}{\pi_i (s) + h (s;\theta_0)} d M_i (s).
\end{align*}
where~$h(\cdot; \theta_0)$ is given by~\eqref{eq:hazardlinear}. Lenglart's inequality implies the second term converges in probability to zero under Assumptions~\ref{E1} and~\ref{E2}. Term (II) satisfies
\begin{align*}
  &n^{-1} \left \| \hat U_n (\theta_0) - \tilde U_n (\theta_0) \right \| \\
  \leq & M n^{-1} \sum_{i=1}^n \sum_{t \in \bfT_i \cup \bfD_i} \bigg \| g
         \left( \tilde W_{i,t}^\top \theta  + \sum_{k=K_x+1}^\infty \hat
         c_{i,k} (t) \int_{t-\Delta}^t \hat \psi_k (s) \phi (s)^\top b
         + \log (\pi_i (t) ) \right) - g \left( \tilde W_{i,t}^\top
         \theta + \log (\pi_i (t)) \right) \bigg \| \\
&\leq M n^{-1} \sum_{i=1}^n \sum_{t \in \bfT_i \cup \bfD_i}
    \sup_{x \in \mathbb{R}} \left \| g^\prime \left( x \right)
  \right\| \times \left \| \sum_{k=K_x+1}^\infty \hat c_{i,k} (t)
  \sum_{l=1}^{K_b} \int_{t-\Delta}^t \hat \psi_k (s) \phi_l (s) b_l
  \right \| \\
&= \frac{M}{4} n^{-1} \sum_{i=1}^n \sum_{t \in \bfT_i \cup \bfD_i}
  \sum_{l=1}^{K_b} \left \| \int_{t-\Delta}^t
  \left( X(t,s) - \sum_{k=1}^{K_x} \hat c_{i,k} (t) \psi_k (s) \right)
  \phi_l (s) b_l\right \| \\
&\to \frac{M}{4} \int_0^\tau \sum_{l=1}^{K_b} \left \| \int_{t-\Delta}^t
  \left( X(t,s) - \sum_{k=1}^{K_x} \hat c_{i,k} (t) \psi_k (s) \right)
  \phi_l (s) b_l\right \| (f_0(t) + f_1(t)) dt
\end{align*}
where~$M = \sup \| \tilde W_{i,t} \|$,~$g(x) = 1/(1+\exp(-x))$ is the
expit function.
\textcolor{blue}{The first inequality is simply due to bringing the metric inside the summand. This allows us to upper bound the difference as a sum over differences in the truncated representation and the true representation.}  The second inequality is due to the Taylor remainder theorem \textcolor{blue}{applied to this difference. This allows us to upper bound the difference as a product of the impact of the non-linear transformation $g$, and the error due to truncation.} The third is due to~$g^\prime (x) = e^x/(1+e^x)^2 \leq e^0/(1+e^0)^2 = 1/4$, reordering the summation, and rewriting the error term in terms of the difference between~$X(t,s)$ and the approximation with truncation level~$K_x$. Letting~$n \to \infty$,  \textcolor{blue}{we can rewrite $n^{-1} \sum_{i=1} \sum_{t \in {\bf T \cup D}}$ as an integral with respect to the joint event and sampling distributions~$(f_0(t) + f_1 (t))$}. Finally, under Assumptions~\ref{assumption:truncation}, \cite{Park2018} show
\[
X(t,s) - \sum_{k=1}^{K_x} \hat c_{i,k} (t) \psi_k (s) \overset{P}{\to} 0
\]
as~$K_x \to \infty$, which implies the third term goes to zero as the truncation level goes to infinity. The same argument can be used in conjunction under assumptions~\ref{E1} and~\ref{E4} to prove~\eqref{eq:andersen2}.

@@

\subsection{Additional Figures}
\label{app:addtlfigs}

\begin{figure}[!th]
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.8\linewidth]{../figures/smoothed_eda_nonevents.png}
  \caption{Electrodermal activity (EDA)}
  \label{fig:mean_eda_nonevents}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.8\linewidth]{../figures/smoothed_ai_nonevents.png}
  \caption{Activity Index (AI)
}  \label{fig:mean_acc_nonevents}
\end{subfigure}
\caption{Mean EDA and AI at non-event times. Note: Due to the data size, non-event times for EDA were further sub-sampled to be maximum 1000 non-event times per individual which leads to the increased variation relative to AI plot}
\label{fig:mean_edacc_nonevents}
\end{figure}
